R-LIME: Rectangular Constraints and Optimization for Local Interpretable Model-agnostic Explanation Methods

### 2024-02-27 paper/paper.tex
Adapt paper.tex for graduation thesis

\documentclass[runningheads]{llncs}

@@

% Authentic title
\title{%
	R-LIME: Rectangular Constraints and Optimization for Local Interpretable
	Model-agnostic Explanation Methods}

% Abbreviated title for the running head
\titlerunning{%
	R-LIME: Rectangular Constraints and Optimization for LIME Methods
}

@@

% The authors' affiliations
\institute{Division of Computer Science and Information Technology\\
	Graduate School of Information Sci.\ and Tech.,
	Hokkaido University\\
	Sapporo 060-0814, JAPAN,\\
	\email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}

@@

% The abstract should briefly summarize the contents of the paper in
% 150--250 words.
\begin{abstract}
	In recent years,
	complex machine learning models such as deep neural networks
	have been used in various industrial fields due to their high accuracy.
	However,
	its complexity has been a major obstacle to implementation
	in decision-making situations where transparency of the decision process
	is required.
	In order to address this problem,
	various post-hoc explanation methods have been proposed,
	but they have not been able to achieve interpretability of
	both the explanation and its scope.
	We propose a new method, R-LIME,
	which interprets complex classifiers in an interpretable scope.
	R-LIME locally approximizes a complex decision boundary linearly
	in a rectangular region
	and maximizes the region as long as the accuracy of the linear
	classifier is higher than a specified threshold.
	The resulting rectangular region is interpretable for users because it is
	expressed as a conjunction of feature predicates.
	We demonstrate the effectiveness of the proposed method through qualitative
	and quantitative experiments using a real-world dataset.
	Finally, we discuss limitations and future work of the proposed method.
	% 148 words
	\keywords{Interpretable machine learning \and Local surrogate model}
\end{abstract}

@@

\begin{figure}[tbp]
	\def\scale{0.38}
	\centering
	\vspace{0.5cm}
	\begin{subfigure}[t]{0.55\textwidth}
		\centering
		\includegraphics[scale=\scale]{example-instance}
		\caption{Focal point.}\label{fig:example-instance}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-lime}
			\caption{%
				Explanation by LIME\@.
				It provides contributions of each feature to the output,
				but does not explicitly indicate its scope.
			}\label{fig:example-lime}
			\vspace{0.4cm}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-anchor}
			\caption{%
				Explanation by Anchor.
				It provides the effective scope of the explanation,
				but does not show the influence of each feature.
			}\label{fig:example-anchor}
		\end{subfigure}
	\end{subfigure}
	\hspace{0.3cm}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\vspace{-2.24cm}
		\includegraphics[scale=\scale]{example-rlime}
		\caption{%
			Explanation by R-LIME\@.
			It provides both contributions of each feature and
			its effective scope.
		}\label{fig:example-rlime}
	\end{subfigure}
	\caption{%
		Example of explanations by LIME~\cite{ribeiro2016why},
		Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
		for a sentiment prediction model.
	}\label{fig:example}
\end{figure}
In this paper,
we focus on local model-agnostic methods.
An example of explanations by LIME and Anchor
for a sentiment prediction model is illustrated in \cref{fig:example}.
LIME~\cite{ribeiro2016why} approximates the complex decision boundary
locally using a linear model around the given focal point,
then provides the weights of the linear model as the contribution of each feature
to the output.
The explanation by LIME (\cref{fig:example-lime}) provides suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For example,
user may apply the insights derived from the explanation
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is incorrect obviously.
Anchor~\cite{ribeiro2018anchors} represents a rectangular region
containing the focal point,
that maximizes the probability of the black-box classifier outputting
the same label as the focal point.
While Anchor provides an effective scope of the explanation,
the information it includes is less than LIME,
limiting its utility~\cite{ribeiro2018anchors}.
The explanation by Anchor (\cref{fig:example-anchor})
suggests that changing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME.

@@

\section{Proposed Method}
\begin{figure}[tbp]
	\centering
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-lime}
		\caption{%
			LIME: Locally approximates the decision boundary around the focal point.
		}\label{fig:lime}
	\end{subfigure}%
	\hspace{0.03\textwidth}
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-anchor}
		\caption{%
			Anchor: Maximizes coverage of a rectangular region
			containing the focal point under accuracy constraints.
		}\label{fig:anchor}
	\end{subfigure}
	\hspace{0.03\textwidth}
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-rlime}
		\caption{%
			R-LIME:
			Maximizes coverage of a rectangular region containing the focal point
			under lower constraints on the accuracy of the linear classifier.
		}\label{fig:rlime}
	\end{subfigure}
	\caption{%
		Visual comparison of LIME, Anchor and R-LIME (our proposed method).
		The solid line represents the rectangular region containing the focal
		point, and the dashed line represents the learned approximation model.
	}
\end{figure}
\subsection{Previous Work}
We specifically focuses on \emph{local} and \emph{model-agnostic} methods.
In this section,
we briefly review existing research on local model-agnostic explanations,
particularly focusing on studies closely related to our proposed method.
\subsubsection{%
	LIME (Local Interpretable Model-agnostic Explanations)
	\cite{ribeiro2016why}
}
LIME locally
approximates a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$
around a focal point $x \in \mathbb{R}^d$
by a linear classifier $g: \mathbb{R}^d \to \{0,1\}$
(\cref{fig:lime}).
The process involves:
\begin{enumerate}
	\item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$
	      and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
	\item Learning a linear classifier $g$
	      using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$
	      by minimizing the following loss function:
	      \begin{equation}
		      \label{eq:lime_loss}
		      \mathcal{L}(f,g,\pi_x)=\sum_{z\in\mathcal{Z}_p}
		      \pi_x(z){\left(f(z)-g(z)\right)}^2,
	      \end{equation}
	      where $\pi_x(z)$ is a weight function designed to be larger for samples
	      closer to $x$, typically implemented using an exponential kernel.
\end{enumerate}

@@

\subsubsection{Anchor~\cite{ribeiro2018anchors}}\label{sec:anchor}
Anchor represents a rectangular region containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule),
that maximizes the probability of the black-box classifier $f$
outputting $f(x)$ within the region.
It aims to highlight important features
contributing significantly to the output (\cref{fig:anchor}).

@@

\subsection{Overview}
We propose R-LIME,
a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
and Anchor~\cite{ribeiro2018anchors}.
Our method locally approximates the given black-box classifier $f$
around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
but samples perturbation from a rectangular region similar to Anchor
so that the generality of approximation is explicitly provided
(\cref{fig:rlime}).
The accuracy of $g$ is defined as the "accuracy" of the rule,
and the generality of explanations is defined as the "coverage" of the rule.

@@

\subsection{Algorithm}\label{sec:alg}
{%
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.32\textwidth]{rlime1}
		\includegraphics[width=0.32\textwidth]{rlime2}
		\includegraphics[width=0.32\textwidth]{rlime3}
		\caption{%
			Overview of the R-LIME algorithm.
			The progression of the algorithm is illustrated from left to right.
			The solid line represents the rectangular region $A$,
			and the dashed line represents the linear approximation model $g$
			learned within $A$.
			The initial value of $A$ is an empty rule (entire input space),
			and predicates are added to $A$, reducing coverage.
			The process continues until $\Prec(A)\ge\tau$,
			at which point the rule with the maximum coverage is output.
		}
	\end{figure}
	\begin{algorithm}[p]
		\input{alg1}
	\end{algorithm}
	\begin{algorithm}[p]
		\input{alg2}
	\end{algorithm}
	\def\myidt{\hspace{\algorithmicindent}}
	\begin{algorithm}[p]
		\input{alg3}
	\end{algorithm}
	\begin{algorithm}[p]
		\input{alg4}
	\end{algorithm}
}

@@

\subsection{Computational Complexity}
Post-hoc explanation methods including LIME, Anchor, and R-LIME
need to query the black-box model multiple times
to get labels for perturbed samples, which is computationally expensive.
The number of queries required for LIME is $|\mathcal{Z}_p|$,
where $|\mathcal{Z}_p|$ is the number of perturbed samples.
On the other hand, the number of queries required for Anchor and R-LIME
is $|\mathcal{D}|$,

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
	\renewcommand{\arraystretch}{1.05}
	\begin{table}[tbp]
		\centering
		\caption{%
			Attributes of the recidivism dataset used in the experiments.
			Continuous features are all discretized,
			and only binary and ordinal features are considered.
		}\label{tab:rcdv}
		\begin{tabular}{llc}
			\toprule
			Attribute              & Overview                              & \# of Possible Values \\
			\midrule
			Race                   & Race (Black or White)                 & 2                     \\
			Alcohol                & Presence of serious alcohol issues    & 2                     \\
			Junky                  & Drug usage                            & 2                     \\
			Supervised Release     & Supervised release                    & 2                     \\
			Married                & Marital status                        & 2                     \\
			Felony                 & Felony or not                         & 2                     \\
			WorkRelease            & Participation in work release program & 2                     \\
			Crime against Property & Crime against property or not         & 2                     \\
			Crime against Person   & Crime against a person or not         & 2                     \\
			Gender                 & Gender (Female or Male)               & 2                     \\
			Priors                 & Number of prior offenses              & 4                     \\
			YearsSchool            & Years of formal education completed   & 4                     \\
			PrisonViolations       & Number of prison rule violations      & 3                     \\
			Age                    & Age                                   & 4                     \\
			MonthsServed           & Months served in prison               & 4                     \\
			\midrule
			Recidivism             & Recidivism or not                     & 2                     \\
			\bottomrule
		\end{tabular}
	\end{table}
}

@@

		{%
			\def\AB#1{\ifnum#1=0 A\else B\fi}
			\def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
			\renewcommand{\arraystretch}{1.02}
			\begin{figure}[tbp]
				\foreach\a in {0,1}{%
						\centering
						\begin{subfigure}{\textwidth}
							\centering
							\begin{tabular}{p{14em}m{16em}}
								\toprule
								\csvreader[no head, late after line= \\]{%
									\dir/\index{\a}.csv
								}{}{%
								\ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii
								}
								\bottomrule
							\end{tabular}
							\caption{Instance~\AB{\a}}\mylabel{\a}
							\vspace{15pt}
						\end{subfigure}
					}
				\vspace{-15pt}
				\caption{Two instances sampled from recidivism dataset.}\label{fig:instance}
			\end{figure}
		}
		{%
			\def\scale{0.315}
			\def\imgwidth{0.495\textwidth}
			\def\hspacebase{\hspace{-1.5em}}
			\def\vspacebase{\vspace{0.5em}}
			\def\vspacebeforecaption{\vspace{-0.4em}}
			\begin{figure}[p]
				\centering
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/lime-\Asample}
					\vspacebeforecaption
					\caption{LIME}\label{fig:A-lime}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\hspace{1.0em}
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
				\end{subfigure}
				\caption{Explanation for Instance A by LIME and R-LIME.}\label{fig:A}
			\end{figure}
			\begin{figure}[p]
				\centering
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/lime-\Bsample}
					\vspacebeforecaption
					\caption{LIME}\label{fig:B-lime}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\hspace{0em}
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
				\end{subfigure}
				\caption{Explanation for Instance B by LIME and R-LIME}\label{fig:B}
			\end{figure}
		}
	}
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each attribute name represent the contribution
(weights of the learned linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures also display the 5 attributes with the highest absolute contribution.

@@

\section{Challenges and Future Perspectives}
 {%
  \def\imgwidth{0.49\textwidth}
  \def\scale{0.08}
  \begin{figure}[t]
	  \centering
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime}
		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
	  \end{subfigure}
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime_for_imbalanced_data}
		  \caption{R-LIME for imbalanced label distribution.
		  }\label{fig:imbalanced}
	  \end{subfigure}
	  \caption{%
		  Behavior of R-LIME for balanced and imbalanced label distribution.
		  In case of imbalanced label distribution,
		  the approximation region covers the entire input space and the
		  linear approximation model always outputs the majority label.
	  }
  \end{figure}
 }

@@

% \subsection{Evaluation through User Studies}
% Given the nature of the field of "interpretable machine learning,"
% where the goal is to "interpret" machine learning models,
% it is challenging to quantitatively compare various methods.
% While quantitative experiments were conducted in \cref{sec:exp2},
% they mainly demonstrated that the proposed method generates
% locally accurate explanations compared to LIME.
% The results do not directly prove the high interpretability of the proposed method.
% 
% One potential method to quantitatively evaluate "interpretability" is
% through user studies.
% For example, \cite{ribeiro2018anchors} conducted user studies,
% assuming that if users could predict the output of a black-box model
% with high accuracy based on provided explanations,
% those explanations contained valuable information about the model's behavior.
% Similarly,
% conducting user studies in this research would be desirable
% to evaluate the interpretability of the proposed method.

>>>>

\def\mode{0} % 0: Graduation thesis, 1: ICPR paper

\ifnum\mode=0
	\documentclass{article}
	\usepackage{prmlthesis}
\else
	\documentclass[runningheads]{llncs}
\fi

@@

\ifnum\mode=0
	\title{%
		R-LIME: Rectangular Constraints and Optimization for Local Interpretable
		Model-agnostic Explanation Methods
	}
	\etitle{}
	\author{Genji Ohara}
	\institute{hogehoge}
\else
	\title{%
		R-LIME: Rectangular Constraints and Optimization for Local Interpretable
		Model-agnostic Explanation Methods}
	% Abbreviated title for the running head
	\titlerunning{%
		R-LIME: Rectangular Constraints and Optimization for LIME Methods
	}

@@

	% The authors' affiliations
	\institute{Division of Computer Science and Information Technology\\
		Graduate School of Information Sci.\ and Tech.,
		Hokkaido University\\
		Sapporo 060-0814, JAPAN,\\
		\email{\{genji-ohara, kimura5, mine\}@ist.hokudai.ac.jp}}
\fi

@@

\ifnum\mode=0
	\pagestyle{plain}
	\pagenumbering{roman}
	\tableofcontents
	\newpage
	\listoffigures\listoftables\clearpage
	\AddToHook{cmd/section/before}{\clearpage}
	\pagestyle{plain}
	\pagenumbering{arabic}
\else

	% The abstract should briefly summarize the contents of the paper in
	% 150--250 words.
	\begin{abstract}
		In recent years,
		complex machine learning models such as deep neural networks
		have been used in various industrial fields due to their high accuracy.
		However,
		its complexity has been a major obstacle to implementation
		in decision-making situations where transparency of the decision process
		is required.
		In order to address this problem,
		various post-hoc explanation methods have been proposed,
		but they have not been able to achieve interpretability of
		both the explanation and its scope.
		We propose a new method, R-LIME,
		which interprets complex classifiers in an interpretable scope.
		R-LIME locally approximizes a complex decision boundary linearly
		in a rectangular region
		and maximizes the region as long as the accuracy of the linear
		classifier is higher than a specified threshold.
		The resulting rectangular region is interpretable for users because it is
		expressed as a conjunction of feature predicates.
		We demonstrate the effectiveness of the proposed method through qualitative
		and quantitative experiments using a real-world dataset.
		Finally, we discuss limitations and future work of the proposed method.
		% 148 words
		\keywords{Interpretable machine learning \and Local surrogate model}
	\end{abstract}
\fi

@@

\begin{figure}[tbp]
	\def\scale{0.38}
	\centering
	\vspace{0.5cm}
	\begin{subfigure}[t]{0.55\textwidth}
		\centering
		\includegraphics[scale=\scale]{example-instance}
		\caption{Focal point.}\label{fig:example-instance}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.45\textwidth}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-lime}
			\caption{%
				Explanation by LIME\@.
				It provides contributions of each feature to the output,
				but does not explicitly indicate its scope.
			}\label{fig:example-lime}
			\vspace{0.4cm}
		\end{subfigure}
		\begin{subfigure}[t]{\textwidth}
			\centering
			\includegraphics[scale=\scale]{example-anchor}
			\caption{%
				Explanation by Anchor.
				It provides the effective scope of the explanation,
				but does not show the influence of each feature.
			}\label{fig:example-anchor}
		\end{subfigure}
	\end{subfigure}
	\hspace{0.3cm}
	\begin{subfigure}[t]{0.45\textwidth}
		\centering
		\vspace{-2.24cm}
		\includegraphics[scale=\scale]{example-rlime}
		\caption{%
			Explanation by R-LIME\@.
			It provides both contributions of each feature and
			its effective scope.
		}\label{fig:example-rlime}
	\end{subfigure}
	\caption[Example of explanations by LIME, Anchor and R-LIME]{%
		Example of explanations by LIME~\cite{ribeiro2016why},
		Anchor~\cite{ribeiro2018anchors} and R-LIME (our proposed method).
		for a sentiment prediction model.
	}\label{fig:example}
\end{figure}
In this paper,
we focus on local model-agnostic methods.
An example of explanations by LIME and Anchor
for a sentiment prediction model is illustrated in \cref{fig:example}.
LIME~\cite{ribeiro2016why} approximates the complex decision boundary
locally using a linear model around the given focal point,
then provides the weights of the linear model as the contribution of each feature
to the output.
The explanation by LIME (\cref{fig:example-lime}) provides suggests that
the word ``not'' mainly contributes to the positive prediction,
but does not explicitly indicate the effective scope.
Without the scope,
users might mistakenly apply the knowledge derived from the explanation
to other instances far from the focal point,
potentially leading to misunderstanding of the black-box model's behavior
\cite{ribeiro2018anchors}.
For example,
user may apply the insights derived from the explanation
to the sentence ``This book is not good.''
and mistakenly conclude that the word ``not''
mainly contributes to the positive prediction for this sentence as well,
which is incorrect obviously.
Anchor~\cite{ribeiro2018anchors} represents a rectangular region
containing the focal point,
that maximizes the probability of the black-box classifier outputting
the same label as the focal point.
While Anchor provides an effective scope of the explanation,
the information it includes is less than LIME,
limiting its utility~\cite{ribeiro2018anchors}.
The explanation by Anchor (\cref{fig:example-anchor})
suggests that changing words other than ``not'' and ``bad''
has little impact on the classifier's output.
While it clearly cannot be applied to the sentence ``This book is not good''
because of not including the word ``bad'',
the explanation does not provide details about the influence of each word,
resulting in less user insight into the model's behavior compared to LIME.

@@

\section{Proposed Method}
\begin{figure}[tbp]
	\centering
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-lime}
		\caption{%
			LIME: Locally approximates the decision boundary around the focal point.
		}\label{fig:lime}
	\end{subfigure}%
	\hspace{0.03\textwidth}
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-anchor}
		\caption{%
			Anchor: Maximizes coverage of a rectangular region
			containing the focal point under accuracy constraints.
		}\label{fig:anchor}
	\end{subfigure}
	\hspace{0.03\textwidth}
	\begin{subfigure}[t]{0.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{visual-rlime}
		\caption{%
			R-LIME:
			Maximizes coverage of a rectangular region containing the focal point
			under lower constraints on the accuracy of the linear classifier.
		}\label{fig:rlime}
	\end{subfigure}
	\caption[Visual comparison of LIME, Anchor and R-LIME]{%
		Visual comparison of LIME, Anchor and R-LIME (our proposed method).
		The solid line represents the rectangular region containing the focal
		point, and the dashed line represents the learned approximation model.
	}
\end{figure}
\subsection{Previous Work}
We specifically focuses on \emph{local} and \emph{model-agnostic} methods.
In this section,
we briefly review existing research on local model-agnostic explanations,
particularly focusing on studies closely related to our proposed method.
\subsubsection[LIME]{%
	LIME (Local Interpretable Model-agnostic Explanations)
	\cite{ribeiro2016why}
}
LIME locally
approximates a trained black-box classifier $f: \mathbb{R}^d \to \{0,1\}$
around a focal point $x \in \mathbb{R}^d$
by a linear classifier $g: \mathbb{R}^d \to \{0,1\}$
(\cref{fig:lime}).
The process involves:
\begin{enumerate}
	\item Obtaining a set of perturbed samples $\mathcal{Z}_p$ around $x$
	      and the set of pseudo-labels $f(\mathcal{Z}_p) = \{f(z) \mid z \in \mathcal{Z}_p\}$.
	\item Learning a linear classifier $g$
	      using $\mathcal{Z}_p$ and $f(\mathcal{Z}_p)$
	      by minimizing the following loss function:
	      \begin{equation}
		      \label{eq:lime_loss}
		      \mathcal{L}(f,g,\pi_x)=\sum_{z\in\mathcal{Z}_p}
		      \pi_x(z){\left(f(z)-g(z)\right)}^2,
	      \end{equation}
	      where $\pi_x(z)$ is a weight function designed to be larger for samples
	      closer to $x$, typically implemented using an exponential kernel.
\end{enumerate}

@@

\subsubsection[Anchor]{%
	Anchor~\cite{ribeiro2018anchors}
}\label{sec:anchor}
Anchor represents a rectangular region containing the focal point $x$,
expressed as a conjunction of feature predicates (a rule),
that maximizes the probability of the black-box classifier $f$
outputting $f(x)$ within the region.
It aims to highlight important features
contributing significantly to the output (\cref{fig:anchor}).

@@

\subsection{Overview}
We propose R-LIME,
a method that aims to address the limitations of LIME~\cite{ribeiro2016why},
and Anchor~\cite{ribeiro2018anchors}.
Our method locally approximates the given black-box classifier $f$
around the focal point $x$ by a linear classifier $g$ similar to LIME and BELLA,
but samples perturbation from a rectangular region similar to Anchor
so that the generality of approximation is explicitly provided
(\cref{fig:rlime}).
The accuracy of $g$ is defined as the ``accuracy'' of the rule,
and the generality of explanations is defined as the ``coverage'' of the rule.

@@

\subsection{Algorithm}\label{sec:alg}
{%
	\begin{figure}[t]
		\centering
		\includegraphics[width=0.32\textwidth]{rlime1}
		\includegraphics[width=0.32\textwidth]{rlime2}
		\includegraphics[width=0.32\textwidth]{rlime3}
		\caption[Overview of the R-LIME algorithm]{%
			Overview of the R-LIME algorithm.
			The progression of the algorithm is illustrated from left to right.
			The solid line represents the rectangular region $A$,
			and the dashed line represents the linear approximation model $g$
			learned within $A$.
			The initial value of $A$ is an empty rule (entire input space),
			and predicates are added to $A$, reducing coverage.
			The process continues until $\Prec(A)\ge\tau$,
			at which point the rule with the maximum coverage is output.
		}
	\end{figure}
	\def\myidt{\hspace{\algorithmicindent}}
	\ifnum\mode=0
		\begin{algorithm}[t]
			\small
			\input{alg1}
		\end{algorithm}
	\else
		\begin{algorithm}[p]
			\small
			\input{alg1}
		\end{algorithm}
	\fi

	\foreach \alg in {2,3,4}{%
			\begin{algorithm}[p]
				\small
				\input{alg\alg}
			\end{algorithm}
		}
}

@@

\ifnum\mode=1
	\subsection{Computational Complexity}
	Post-hoc explanation methods including LIME, Anchor, and R-LIME
	need to query the black-box model multiple times
	to get labels for perturbed samples, which is computationally expensive.
	The number of queries required for LIME is $|\mathcal{Z}_p|$,
	where $|\mathcal{Z}_p|$ is the number of perturbed samples.
	On the other hand, the number of queries required for Anchor and R-LIME
	is $|\mathcal{D}|$,
\fi

@@

\subsection{Qualitative Evaluation}
\subsubsection{Experimental Setup}\label{sec:exp_setting}
{%
	\renewcommand{\arraystretch}{1.05}
	\begin{table}[tbp]
		\centering
		\caption[Attributes of the recidivism dataset used in the experiments]{%
			Attributes of the recidivism dataset used in the experiments.
			Continuous features are all discretized,
			and only binary and ordinal features are considered.
		}\label{tab:rcdv}
		\ifnum\mode=0
			\small
		\fi
		\begin{tabular}{llc}
			\toprule
			Attribute              & Overview                              & \# of \ifnum\mode=1 Possible \fi Values \\
			\midrule
			Race                   & Race (Black or White)                 & 2                                       \\
			Alcohol                & Presence of serious alcohol issues    & 2                                       \\
			Junky                  & Drug usage                            & 2                                       \\
			Supervised Release     & Supervised release                    & 2                                       \\
			Married                & Marital status                        & 2                                       \\
			Felony                 & Felony or not                         & 2                                       \\
			WorkRelease            & Participation in work release program & 2                                       \\
			Crime against Property & Crime against property or not         & 2                                       \\
			Crime against Person   & Crime against a person or not         & 2                                       \\
			Gender                 & Gender (Female or Male)               & 2                                       \\
			Priors                 & Number of prior offenses              & 4                                       \\
			YearsSchool            & Years of formal education completed   & 4                                       \\
			PrisonViolations       & Number of prison rule violations      & 3                                       \\
			Age                    & Age                                   & 4                                       \\
			MonthsServed           & Months served in prison               & 4                                       \\
			\midrule
			Recidivism             & Recidivism or not                     & 2                                       \\
			\bottomrule
		\end{tabular}
	\end{table}
}

@@

		{%
			\def\AB#1{\ifnum#1=0 A\else B\fi}
			\def\mylabel#1{\ifnum#1=0 \label{fig:A-instance}\else \label{fig:B-instance}\fi}
			\ifnum\mode=0
				\renewcommand{\arraystretch}{0.99}
			\else
				\renewcommand{\arraystretch}{1.02}
			\fi
			\begin{figure}[tbp]
				\foreach\a in {0,1}{%
						\centering
						\begin{subfigure}{\textwidth}
							\ifnum\mode=0
								\small
							\fi
							\centering
							\begin{tabular}{p{14em}m{16em}}
								\toprule
								\csvreader[no head, late after line= \\]{%
									\dir/\index{\a}.csv
								}{}{%
								\ifnum\thecsvrow=16 \midrule\fi\csvcoli & \csvcolii
								}
								\bottomrule
							\end{tabular}
							\caption{Instance~\AB{\a}}\mylabel{\a}
							\vspace{15pt}
						\end{subfigure}
					}
				\vspace{-15pt}
				\caption[Two instances sampled from recidivism dataset]{%
					Two instances sampled from recidivism dataset.
				}\label{fig:instance}
			\end{figure}
		}
		{%
			\ifnum\mode=0
				\def\scale{0.3}
				\def\imgwidth{0.45\textwidth}
			\else
				\def\scale{0.315}
				\def\imgwidth{0.495\textwidth}
			\fi
			\def\hspacebase{\hspace{-1.5em}}
			\def\vspacebase{\vspace{0.5em}}
			\def\vspacebeforecaption{\vspace{-0.4em}}
			\begin{figure}[p]
				\centering
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/lime-\Asample}
					\vspacebeforecaption
					\caption{LIME}\label{fig:A-lime}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\hspace{1.0em}
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-70}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.70$)}\label{fig:A-rlime-70}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-80}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.80$)}\label{fig:A-rlime-80}
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Asample-90}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.90$)}\label{fig:A-rlime-90}
				\end{subfigure}
				\caption[Explanation for Instance A by LIME and R-LIME]{%
					Explanation for Instance A by LIME and R-LIME.
				}\label{fig:A}
			\end{figure}
			\begin{figure}[p]
				\centering
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/lime-\Bsample}
					\vspacebeforecaption
					\caption{LIME}\label{fig:B-lime}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-70}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.70$)}\label{fig:B-rlime-70}
					\vspacebase
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-80}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.80$)}\label{fig:B-rlime-80}
				\end{subfigure}
				\begin{subfigure}[t]{\imgwidth}
					\hspacebase
					\hspace{0em}
					\includegraphics[scale=\scale]{\dir/newlime-\Bsample-90}
					\vspacebeforecaption
					\caption{R-LIME ($\tau=0.90$)}\label{fig:B-rlime-90}
				\end{subfigure}
				\caption[Explanation for Instance B by LIME and R-LIME]{%
					Explanation for Instance B by LIME and R-LIME.
				}\label{fig:B}
			\end{figure}
		}
	}
\subsubsection{Experimental Results}
The results of the experiment are shown in \cref{fig:A,fig:B}.
The values assigned to each attribute name represent the contribution
(weights of the learned linear classifier)
to the output of the black-box classifier,
normalized such that the absolute sum is 1.
The figures also display the 5 attributes with the highest absolute contribution.

@@

\section{Challenges and Future Perspectives}
 {%
  \def\imgwidth{0.49\textwidth}
  \def\scale{0.08}
  \begin{figure}[t]
	  \centering
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime}
		  \caption{R-LIME for balanced label distribution.}\label{fig:balanced}
	  \end{subfigure}
	  \begin{subfigure}[t]{\imgwidth}
		  \centering
		  \includegraphics[scale=\scale]{newlime_for_imbalanced_data}
		  \caption{R-LIME for imbalanced label distribution.
		  }\label{fig:imbalanced}
	  \end{subfigure}
	  \caption[Behavior of R-LIME for balanced and imbalanced label distribution]{%
		  Behavior of R-LIME for balanced and imbalanced label distribution.
		  In case of imbalanced label distribution,
		  the approximation region covers the entire input space and the
		  linear approximation model always outputs the majority label.
	  }
  \end{figure}
 }

@@
